---
title: "Datascience in Everyday Music Listening Portfolio"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

spotify_features %>% 
  ggplot(aes(x = loudness)) +
  geom_histogram(binwidth = 5)
  
spotify_features %>% 
  ggplot(aes(x = subtype, y = acousticness)) +
  geom_boxplot()
  
spotify_features %>% 
  ggplot(aes(x = type, y = danceability, fill = subtype)) +
  geom_violin()
  
spotify_features %>% 
  ggplot(aes(x = valence, y = energy)) + 
  facet_wrap(~ type) +
  stat_density_2d(
    geom = 'raster', 
    aes(fill = stat(density)), 
    contour = FALSE
  ) + 
  geom_jitter(colour = 'white', alpha = 0.5) + 
  coord_equal()